Explore the SingleR results

### 2025-07-16 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd
we can use the right merge-sce path now that consensus are there

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
ref_dir <- file.path(module_dir, "references")
results_dir <- file.path(module_dir, "results", "singler")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
```

@@

# merged SCE file
# OBTAINED FROM PORTAL DIRECTLY on 2025-07-09
sce_file <- file.path(
  data_dir,
  "SCPCP000004_merged.rds"
)

@@

# RUH ROH!!!
# https://github.com/AlexsLemonade/scpcaTools/issues/298
merged_sce$cell_id <- colnames(merged_sce)
```

>>>>

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
ref_dir <- file.path(module_dir, "references")
results_dir <- file.path(module_dir, "results", "singler")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
merged_dir <- file.path(repository_base, "data", "current", "results", "merge-sce", "SCPCP000004")
```

@@

# merged SCE file
sce_file <- file.path(
  merged_dir,
  "SCPCP000004_merged.rds"
)

@@

# Ensure cell_id is correct
merged_sce$cell_id <- colnames(merged_sce)
```
